Energy and the CES production function

### 2015-08-25 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Changed sigma graph width.

<<sigma_graph_2, fig.pos="H", fig.align='center', fig.width=8.5, fig.height=5, out.width="0.9\\textwidth", fig.cap="Elasticities of substitution~($\\sigma$).">>=
breaks_labels = c(0.01, 0.1, 1, 10, 100)
p <- 
ggplot(
  AllCoeffs %>% 
    gather(type, value, matches("sigma")) %>% 
    filter(!is.na(value)) %>% 
    filter(! type %in% c("sigma", "sigma_1")) %>%
    mutate(nest = plyr::mapvalues(nest, 
                                  from=c("kle", "lek", "ekl"), 
                                  to=c("(kl)e", "(le)k", "(ek)l")),
           type = plyr::mapvalues(type,
                                  from=c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2"),
                                  to  =c("sigma_kl", "sigma_le", "sigma_ek", "sigma_kl_e", "sigma_le_k", "sigma_ek_l")),
           type = relevelFactor(type, c("sigma_kl", "sigma_le", "sigma_ek", "sigma_kl_e", "sigma_le_k", "sigma_ek_l")),
           Model = interaction(nest, CSP, sep = " ", drop=TRUE),
           Inputs = flavor
           )
  ) + 
  geom_point(aes(x=value, y=type, 
                 shape = Model, fill=Model, size=Model,
                 color=Inputs
                 )
                 #position = position_jitter(height=0.2, width=0)
             ) + 
  facet_grid( type ~ Country, scales = "free_y" ) + 
  scale_x_log10(limits = c(0.001,2000), breaks=breaks_labels, labels=breaks_labels) +
  xlab("") +
  geom_vline(xintercept = 1, color="gray50", size=0.2) +
  ylab("") +
  labs(color = "Factors of production") +
  xy_theme() +
  theme(
    legend.position="top",
    strip.text.y = element_blank())

@@

<<sigma_graph_3, fig.pos="H", fig.align='center', fig.width=8.5, fig.height=5, out.width="0.9\\textwidth", fig.cap="Elasticities of substitution~($\\sigma$) with factors of production on the vertical facet.">>=
breaks_labels = c(0.01, 0.1, 1, 10, 100)
p <- 
  ggplot(
    AllCoeffs %>% 
      gather(type, value, matches("sigma")) %>% 
      filter(!is.na(value)) %>% 
      filter(! type %in% c("sigma", "sigma_1")) %>%
      mutate(nest = plyr::mapvalues(nest, 
                                    from=c("kle", "lek", "ekl"), 
                                    to=c("(kl)e", "(le)k", "(ek)l")),
             Model = interaction(nest, CSP, sep = " ", drop=TRUE),
             Inputs = flavor,
             type = plyr::mapvalues(type,
                                    from=c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2"),
                                    to  =c("sigma_kl", "sigma_le", "sigma_ek", "sigma_kl_e", "sigma_le_k", "sigma_ek_l")),
             type = relevelFactor(type, rev(c("sigma_kl", "sigma_le", "sigma_ek", "sigma_kl_e", "sigma_le_k", "sigma_ek_l")))
             )
    ) + 
  geom_point(aes(x=value, y=type, 
                 shape = Model, fill=Model, size=Model#,
                 # color=Inputs
                 )
             #position = position_jitter(height=0.2, width=0)
             ) + 
  facet_grid( Inputs ~ Country) + 
  scale_x_log10(limits = c(0.001,2000), breaks=breaks_labels, labels=breaks_labels) +
  xlab("") +
  geom_vline(xintercept = 1, color="gray50", size=0.2) +
  ylab("") +
#   labs(color = "Factors of production") +
  xy_theme()

>>>>

<<sigma_graph_2, fig.pos="H", fig.align='center', fig.width=8.5, fig.height=5, fig.cap="Elasticities of substitution~($\\sigma$).">>=
breaks_labels = c(0.01, 0.1, 1, 10, 100)
p <- 
ggplot(
  AllCoeffs %>% 
    gather(type, value, matches("sigma")) %>% 
    filter(!is.na(value)) %>% 
    filter(! type %in% c("sigma", "sigma_1")) %>%
    mutate(nest = plyr::mapvalues(nest, 
                                  from=c("kle", "lek", "ekl"), 
                                  to=c("(kl)e", "(le)k", "(ek)l")),
           type = plyr::mapvalues(type,
                                  from=c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2"),
                                  to  =c("sigma_kl", "sigma_le", "sigma_ek", "sigma_kl_e", "sigma_le_k", "sigma_ek_l")),
           type = relevelFactor(type, c("sigma_kl", "sigma_le", "sigma_ek", "sigma_kl_e", "sigma_le_k", "sigma_ek_l")),
           Model = interaction(nest, CSP, sep = " ", drop=TRUE),
           Inputs = flavor
           )
  ) + 
  geom_point(aes(x=value, y=type, 
                 shape = Model, fill=Model, size=Model,
                 color=Inputs
                 )
                 #position = position_jitter(height=0.2, width=0)
             ) + 
  facet_grid( type ~ Country, scales = "free_y" ) + 
  scale_x_log10(limits = c(0.001,2000), breaks=breaks_labels, labels=breaks_labels) +
  xlab("") +
  geom_vline(xintercept = 1, color="gray50", size=0.2) +
  ylab("") +
  labs(color = "Factors of production") +
  xy_theme() +
  theme(
    legend.position="top",
    strip.text.y = element_blank())

@@

<<sigma_graph_3, fig.pos="H", fig.align='center', fig.width=8.5, fig.height=5, fig.cap="Elasticities of substitution~($\\sigma$) with factors of production on the vertical facet.">>=
breaks_labels = c(0.01, 0.1, 1, 10, 100)
p <- 
  ggplot(
    AllCoeffs %>% 
      gather(type, value, matches("sigma")) %>% 
      filter(!is.na(value)) %>% 
      filter(! type %in% c("sigma", "sigma_1")) %>%
      mutate(nest = plyr::mapvalues(nest, 
                                    from=c("kle", "lek", "ekl"), 
                                    to=c("(kl)e", "(le)k", "(ek)l")),
             Model = interaction(nest, CSP, sep = " ", drop=TRUE),
             Inputs = flavor,
             type = plyr::mapvalues(type,
                                    from=c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2"),
                                    to  =c("sigma_kl", "sigma_le", "sigma_ek", "sigma_kl_e", "sigma_le_k", "sigma_ek_l")),
             type = relevelFactor(type, rev(c("sigma_kl", "sigma_le", "sigma_ek", "sigma_kl_e", "sigma_le_k", "sigma_ek_l")))
             )
    ) + 
  geom_point(aes(x=value, y=type, 
                 shape = Model, fill=Model, size=Model#,
                 # color=Inputs
                 )
             #position = position_jitter(height=0.2, width=0)
             ) + 
  facet_grid( Inputs ~ Country) + 
  scale_x_log10(limits = c(0.001,2000), breaks=breaks_labels, labels=breaks_labels) +
  xlab("") +
  geom_vline(xintercept = 1, color="gray50", size=0.2) +
  ylab("") +
#   labs(color = "Factors of production") +
  xy_theme()
